Respiratory oacsteroids

### 2021-02-16 r_notebooks/preparing_famot.Rmd
Typos

---
title: "Respiratory famotsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

@@

@@

## Monthly summary by GP
famot_monthly_quantity_gp <- 
  countRegional(famot, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

>>>>

---
title: "Famotodine"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

@@

* Daily quantity per 10,000,000 patients due to low prescribing volumes

@@

## Monthly summary by GP
famot_monthly_quantity_gp <- 
  countRegional(famot, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 10000000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

### 2021-02-16 r_notebooks/preparing_oac_prop.Rmd
Typos

```{r oac-gp-practice-forecasts}
plan(cluster)
system.time(oac_gp_fcsts <-
              oac_monthly_prop_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcstsBound(h = "6 months"))
plan(sequential)

>>>>

```{r oac-gp-practice-forecasts}
plan(cluster)
system.time(oac_gp_fcsts <-
              oac_monthly_prop_gp_pre_cv19 %>%
              regionalJointFcstsBound(h = "6 months"))
plan(sequential)
